### 2024-07-30 getting-started.qmd
20240730 - identify duplicates

nfl_advancedStatsPFR_weekly <- nfl_advancedStatsPFR_weekly %>% 
  rename(pfr_id = pfr_player_id)

nfl_advancedStatsPFR_seasonal <- left_join(
  nfl_advancedStatsPFR_seasonal,
  nfl_playerIDs %>% 
    filter(!is.na(pfr_id)) %>% 
    filter(gsis_id != "00-0039137") %>% # drop DL Byron Young, keep OLB Byron Young
    select(pfr_id, gsis_id) %>% 
    unique(),
  by = "pfr_id"
)

nfl_advancedStatsPFR_weekly <- left_join(
  nfl_advancedStatsPFR_weekly,
  nfl_playerIDs %>% 
    filter(!is.na(pfr_id)) %>% 
    filter(gsis_id != "00-0039137") %>% # drop DL Byron Young, keep OLB Byron Young
    select(pfr_id, gsis_id) %>% 
    unique(),
  by = "pfr_id"
)

>>>>

# Prepare data for merging
nfl_advancedStatsPFR_weekly <- nfl_advancedStatsPFR_weekly %>% 
  rename(pfr_id = pfr_player_id)

# Identify duplicates
nfl_advancedStatsPFR_seasonal %>% 
  select(pfr_id, season, age) %>% 
  na.omit() %>% 
  unique() %>% 
  group_by(pfr_id, season) %>% 
  filter(n() > 1) %>% 
  arrange(pfr_id, season)

# Merge seasonal data with the player IDs
nfl_advancedStatsPFR_seasonal <- left_join(
  nfl_advancedStatsPFR_seasonal,
  nfl_playerIDs %>% 
    filter(!is.na(pfr_id)) %>% 
    filter(gsis_id != "00-0039137") %>% # drop DL Byron Young, keep OLB Byron Young
    select(pfr_id, gsis_id) %>% 
    unique(),
  by = "pfr_id"
)

# Merge weekly data with the player IDs
nfl_advancedStatsPFR_weekly <- left_join(
  nfl_advancedStatsPFR_weekly,
  nfl_playerIDs %>% 
    filter(!is.na(pfr_id)) %>% 
    filter(gsis_id != "00-0039137") %>% # drop DL Byron Young, keep OLB Byron Young
    select(pfr_id, gsis_id) %>% 
    unique(),
  by = "pfr_id"
)
